Recpature distances

### 2024-03-26 recaptureanalysis/recaps.Rmd
Recapture analysis stuff

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
library(tidyverse)
library(readxl)
library(sf)
library(lubridate)
library(spacetools)
library(deltamapr)
load("Recaps.RData")
#save(nndist, distances, recaps, recaps2, recaps3, RVhdist, SCsoft, SChard, RVhdistx, Dwschard, Dwscsoft, file = "Recaps.RData")
```

@@

Fist let's calcualte distance from release location to recapture location.

@@

recaps = read_excel("Recaptured Experimental Release_2022-2023_working draft (2).xlsx", 
                    sheet = "Full DSM Data") %>%
  rename(Site = `Release Site`, Type = `Release Type`, Latitude= `Start Latitude`, Longitude = `Start Longitude`,
         Mark = `VIE Color/Position`)
recaps    =     mutate(recaps, fishID = paste("smelt", 1:nrow(recaps)),
                Type = case_when(Type == "header" ~ "Soft",
                                 is.na(Type) ~ "Wild",
                                 TRUE ~ Type),
                Site = case_when(is.na(Site) ~ "Wild",
                                 TRUE ~ Site))
str(recaps)

@@

#Now make a data frame of the release locations
release = read_excel("releases.xlsx") %>%
  rename(LatitudeR = Latitude, LongitudeR = Longitude)
releasesf = st_as_sf(filter(release, !is.na(LatitudeR)),  coords = c("LongitudeR", "LatitudeR"), crs = 4326)

#merge recap points with release points

recaps2 = left_join(recaps, release) %>%
  mutate(DaysSinceRelease = Date - ReleaseDate)
recapsf = st_as_sf(filter(recaps2, !is.na(`Longitude`)), coords = c("Longitude", "Latitude"), crs = 4326)

@@

```{r, eval=FALSE}
#one release at a time
Dwschard = filter(recaps2, Type == "Hard", Site == "SDWSC")
dwsch = filter(release, Site == "SDWSC", Type == "Hard") %>%
  select(LatitudeR, LongitudeR) %>%
  rename(Latitude = LatitudeR, Longitude = LongitudeR)
tesst = GGdist(Water_map = spacetools::Delta, Points = Dwschard, Latitude_column = `Latitude`,
               Longitude_column = `Longitude`, PointID_column = fishID, EndPoint = dwsch)

#now let's do DWSC soft
Dwscsoft = filter(recaps2, Type == "Soft", Site == "SDWSC")
dwscs = filter(release, Site == "SDWSC", Type == "Soft") %>%
  select(LatitudeR, LongitudeR)%>%
  rename(Latitude = LatitudeR, Longitude = LongitudeR)
tesst2 = GGdist(Water_map = spacetools::Delta, Points = Dwscsoft, Latitude_column = `Latitude`,
               Longitude_column = `Longitude`, PointID_column = fishID, EndPoint = dwscs)

#now let's do Rio Vista hard
RVhard = filter(recaps2, Type == "Hard", Site == "Rio Vista", !is.na(Latitude))
rvh = filter(release, Site == "Rio Vista", Type == "Hard") %>%
  select(LatitudeR, LongitudeR)%>%
  rename(Latitude = LatitudeR, Longitude = LongitudeR) %>%
  distinct()
tesst3 = GGdist(Water_map = spacetools::Delta, Points = RVhard, Latitude_column = `Latitude`,
                Longitude_column = `Longitude`, PointID_column = fishID, EndPoint = rvh)

#now the trailer
RVhardt = filter(recaps2, Type == "Hard (Trailer)", Site == "Rio Vista")
rvht = filter(release, Site == "Rio Vista", Type == "Hard (Trailer)") %>%
  select(LatitudeR, LongitudeR)%>%
  rename(Latitude = LatitudeR, Longitude = LongitudeR)
tesst4 = GGdist(Water_map = spacetools::Delta, Points = RVhardt, Latitude_column = `Latitude`,
                Longitude_column = `Longitude`, PointID_column = fishID, EndPoint = rvht)

distances = bind_rows(tesst, tesst2, tesst3, tesst4)
```

@@

recaps3 = left_join(recaps2, distances) %>%
  mutate(SiteType = paste(Type, Site))

@@

write.csv(recaps, "Recapturedistances.csv")
```

@@

```{r}
ggplot(filter(recaps3, Type != "Hard (Trailer)", Type != "Wild"), aes(x = SiteType, y = Distance))+ 
  geom_boxplot(aes(fill = SiteType))+
  ylab("Distance from Release Site (m)")+
  scale_fill_discrete(guide = NULL)+
  theme_bw()
```

@@

#ANOVA of differences in distance by release group
library(emmeans)
m1 = lm(Distance ~ SiteType, data = recaps3)
summary(m1)
anova(m1)
emmeans(m1, pairwise ~ SiteType)
plot(emmeans(m1, pairwise ~ SiteType), comparisons = T)

#so hard releases at RIo Vista traveled further from hard releases at SDWSC, but no other significant differences

@@

@@

RVhdist = Waterdist(Water_map = spacetools::Delta, Points = RVhardt, Latitude_column = `Latitude`,
                    Longitude_column = `Longitude`, PointID_column = fishID)

RVhdistx = Waterdist(Water_map = spacetools::Delta, Points = RVhard, Latitude_column = `Latitude`,
                    Longitude_column = `Longitude`, PointID_column = fishID)

SCsoft  = Waterdist(Water_map = spacetools::Delta, Points = Dwscsoft, Latitude_column = `Latitude`,
                       Longitude_column = `Longitude`, PointID_column = fishID)

SChard = Waterdist(Water_map = spacetools::Delta, Points = Dwschard, Latitude_column = `Latitude`,
                   Longitude_column = `Longitude`, PointID_column = fishID)

RVhdist
RVhdistx
SCsoft
SChard

@@

Cluster = data.frame(Release = c("RV Hard", "RV Hard Trailer", "DWSC soft", "DWSC hard"),
                     meadist = c(mean(RVhdistx[lower.tri(RVhdistx)]), 
                                 mean(RVhdist[lower.tri(RVhdist)]), 
                                 mean(SCsoft[lower.tri(SCsoft)]), 
                                 mean(SChard[lower.tri(SChard)])),
                     SD = c(sd(RVhdistx), sd(RVhdist), sd(SCsoft), sd(SChard)))

Cluster = mutate(Cluster, CV = SD/meadist)
Cluster
```

@@

RVhdistx[lower.tri(RVhdistx, diag = T)] = NA
RVhdist[lower.tri(RVhdist, diag = T)] = NA
SCsoft[lower.tri(SCsoft, diag = T)] = NA
SChard[lower.tri(SChard, diag = T)] = NA
RVdtx = as.data.frame(RVhdistx) %>%
  mutate(Fish1 = row.names(RVhdistx)) %>%
  pivot_longer(cols = -Fish1, names_to = "Fish2", values_to = "Distance") %>%
  filter(!is.na(Distance)) %>%
  mutate(Release = "Rio Vista Hard")

RVdt = as.data.frame(RVhdist) %>%
  mutate(Fish1 = row.names(RVhdist)) %>%
  pivot_longer(cols = -Fish1, names_to = "Fish2", values_to = "Distance") %>%
  filter(!is.na(Distance)) %>%
  mutate(Release = "Trailer")

SCs = as.data.frame(SCsoft) %>%
  mutate(Fish1 = row.names(SCsoft)) %>%
  pivot_longer(cols = -Fish1, names_to = "Fish2", values_to = "Distance") %>%
  filter(!is.na(Distance)) %>%
  mutate(Release = "DWSC Soft")

SCh = as.data.frame(SChard) %>%
  mutate(Fish1 = row.names(SChard)) %>%
  pivot_longer(cols = -Fish1, names_to = "Fish2", values_to = "Distance") %>%
  filter(!is.na(Distance)) %>%
  mutate(Release = "DWSC Hard")

nndist = bind_rows(RVdtx, RVdt, SCs, SCh) %>%
  mutate(Release = factor(Release, levels = c("Rio Vista Hard", "DWSC Hard", "DWSC Soft", "Trailer"),
                          labels = c("Hard Rio Vista", "Hard SDWSC", "Soft SWDSC", "Trailer")))

ggplot(filter(nndist, Release != "Trailer"), aes(x = Release, y = Distance, fill = Release)) + geom_boxplot()+
  ylab("Distance Between Recaptures")+ theme_bw()+ scale_fill_discrete(guide = NULL)

@@

>>>>

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
library(tidyverse)
library(readxl)
library(sf)
library(lubridate)
library(spacetools)
library(deltamapr)
#load("Recaps.RData")
#save(nndist, distances, recaps, recaps2, recaps3, RVhdist, SCsoft, SChard, RVhdistx, Dwschard, Dwscsoft, file = "Recaps.RData")
```

@@

Fist let's calculate distance from release location to recapture location.

@@

recaps = read_excel("data/Running Delta Smelt Catch.xlsx", 
                    sheet = "Delta Smelt Catch Data") %>%
  rename( Latitude= `LatitudeStart`, Longitude = `LongitudeStart`) %>%
  mutate(FishID = paste("Fish", 1:nrow(recaps))) %>%
  select(-ReleaseDate, -Preservation, -Disposition, -SpecialStudyID, -MarkCode, -Dateknown)

#bring in standaridized release location/mark info
release = read_excel("data/releases_v2.xlsx") %>%
  rename(LatitudeR = Latitude, LongitudeR = Longitude)

recaps2 = left_join(recaps, select(release, -TotalReleased), by = "ReleaseEvent") %>%
  mutate(DaysSinceRelease = SampleDate - ReleaseDate,
         Type = case_when(ReleaseMethod == "Unknown" ~ "Unknown",
                          ReleaseMethod == "NA" ~ "Wild/unmarked",
                          TRUE ~ Type))

str(recaps)

@@

```{r}
releasesf = st_as_sf(filter(release, !is.na(LatitudeR)),  coords = c("LongitudeR", "LatitudeR"), crs = 4326)

#make a spatial data frame of recaptures

recapsf = st_as_sf(filter(recaps2, !is.na(`Longitude`)), coords = c("Longitude", "Latitude"), crs = 4326)

@@

```{r, eval=FALSE}
#one release at a time
Dwschard = filter(recaps2, Type == "Hard (carboy)", Site == "SDWSC")
dwsch = filter(release, Site == "SDWSC", Type == "Hard (carboy)") %>%
  select(LatitudeR, LongitudeR) %>%
  rename(Latitude = LatitudeR, Longitude = LongitudeR)
tesst = GGdist(Water_map = spacetools::Delta, Points = Dwschard, Latitude_column = `Latitude`,
               Longitude_column = `Longitude`, PointID_column = FishID, EndPoint = dwsch)

#now let's do DWSC soft
Dwscsoft = filter(recaps2, Type == "Soft (carboy)", Site == "SDWSC")
dwscs = filter(release, Site == "SDWSC", Type == "Soft (carboy)") %>%
  select(LatitudeR, LongitudeR)%>%
  rename(Latitude = LatitudeR, Longitude = LongitudeR)
tesst2 = GGdist(Water_map = spacetools::Delta, Points = Dwscsoft, Latitude_column = `Latitude`,
               Longitude_column = `Longitude`, PointID_column = FishID, EndPoint = dwscs)

#now let's do Rio Vista hard
RVhard = filter(recaps2,  Site == "Rio Vista", !is.na(Latitude))
rvh = filter(release, Site == "Rio Vista", Type == "Hard (trailer)") %>%
  select(LatitudeR, LongitudeR)%>%
  rename(Latitude = LatitudeR, Longitude = LongitudeR) %>%
  distinct()
tesst3 = GGdist(Water_map = spacetools::Delta, Points = RVhard, Latitude_column = `Latitude`,
                Longitude_column = `Longitude`, PointID_column = FishID, EndPoint = rvh)

# #now the trailer
# RVhardt = filter(recaps2, Type == "Hard (Trailer)", Site == "Rio Vista")
# rvht = filter(release, Site == "Rio Vista", Type == "Hard (Trailer)") %>%
#   select(LatitudeR, LongitudeR)%>%
#   rename(Latitude = LatitudeR, Longitude = LongitudeR)
# tesst4 = GGdist(Water_map = spacetools::Delta, Points = RVhardt, Latitude_column = `Latitude`,
#                 Longitude_column = `Longitude`, PointID_column = fishID, EndPoint = rvht)

distances = bind_rows(tesst, tesst2, tesst3)
```

@@

recaps3 = left_join(recaps2, distances) %>%
  mutate(Type2 = case_when(Type %in% c("Hard (large scale)","Hard (trailer)") ~ "Hard (Large Scale)",
                           TRUE ~ Type)) %>%
  mutate(SiteType = paste(Type, Site))

@@

#load first flush info
ff = read_excel("data/releases_v2.xlsx", sheet = "firstflush")

recaps3 = recaps3 %>%
  mutate(Year = year(SampleDate),
                                BroodYear = case_when(LifeStage %in% c("Adult", "Adult*") & yday(SampleDate) <200 ~ Year-1,
                                     LifeStage == "Juvenile" & yday(SampleDate) <90 ~ Year-1,
                                     TRUE ~ Year)) %>%
         left_join(ff)%>%
         mutate(FFyn = case_when(ReleaseDate > FirstFlush ~ "Yes",
                          TRUE ~ "No"))

write.csv(recaps, "recaptureanalysis/Recapturedistances.csv")
```

@@

```{r}
ggplot(filter(recaps3, Type != "Wild/unmarked", Type != "Unknown"), aes(x = SiteType, y = Distance))+ 
  geom_boxplot(aes(fill = SiteType))+
  ylab("Distance from Release Site (m)")+
  scale_fill_discrete(guide = NULL)+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust =1, vjust =1))
```
now by first flush

ggplot(filter(recaps3, Type != "Wild/unmarked", Type != "Unknown"), aes(x = Type, y = Distance))+ 
  geom_boxplot(aes(fill = SiteType))+
  ylab("Distance from Release Site (m)")+
  scale_fill_discrete(guide = NULL)+
  theme_bw()+
  facet_wrap(~FFyn)+
  theme(axis.text.x = element_text(angle = 45, hjust =1, vjust =1))

Let's consolidate some of the release types...

tots = group_by(recaps3, Type2) %>%
  summarize(N = n())

ggplot(filter(recaps3, Type != "Wild/unmarked", Type != "Unknown"), aes(x = Type2, y = Distance/1000))+ 
  geom_boxplot(aes(fill = Type2))+
  ylab("Distance from Release Site (km)")+
  scale_fill_discrete(guide = NULL)+
  geom_text(data = filter(tots, Type2 != "Wild/unmarked", Type2 != "Unknown"), aes(x = Type2, label = N), y=2, inherit.aes = FALSE)+ xlab(NULL)+
    stat_summary(fun.y=mean, geom="point", shape = 23, fill = "white", size =4) +
  theme_bw()

ggsave("plots/hardvsoft_distance.tiff", device = "tiff", width =6, height =4)

totsby = group_by(recaps3, Type2, BroodYear) %>%
  summarize(N = n())

ggplot(filter(recaps3, Type != "Wild/unmarked", Type != "Unknown"), aes(x = Type2, y = Distance/1000))+ 
  geom_boxplot(aes(fill = Type2))+
  ylab("Distance from Release Site (km)")+
  scale_fill_discrete(guide = NULL)+
  geom_label(data = filter(totsby, Type2 != "Wild/unmarked", Type2 != "Unknown"), 
             aes(x = Type2, label = paste("N=", N)), y=2, inherit.aes = FALSE)+ xlab(NULL)+
    stat_summary(fun.y=mean, geom="point", shape = 23, fill = "white", size =4) +
  facet_wrap(~BroodYear)+
  theme_bw()

ggsave("plots/hardvsoft_distance_BY.tiff", device = "tiff", width =6, height =4)

```{r}
library(ggbeeswarm)

ggplot(filter(recaps3, Type != "Wild/unmarked"), aes(x = Type2, y = Distance))+ 
  geom_quasirandom(aes(color = as.factor(BroodYear), shape = Site))+
  ylab("Distance from Release Site (m)")+
  facet_wrap(~FFyn)+
  scale_fill_discrete(guide = NULL)+
  theme_bw()

ggplot(filter(recaps3, Type != "Wild", BroodYear != 2024), aes(x = Type2, y = Distance))+ 
  geom_quasirandom(aes(color = Type, shape = Site))+
  ylab("Distance from Release Site (m)")+
  scale_fill_discrete(guide = NULL)+
  facet_wrap(~BroodYear)+

  theme_bw()

tots2023 = filter(recaps3, Type != "Wild/unmarked", BroodYear == 2023) %>%
  group_by(Type) %>%
  summarize(N = n()) %>%
  droplevels()

test23 = filter(recaps3, Type != "Wild/unmarked", BroodYear == 2023, !is.na(Distance)) %>%
  droplevels()

ggplot(test23, aes(x = Type, y = Distance))+ 
  geom_boxplot(aes(fill = Type))+
  ylab("Distance from Release Site (m)")+
  scale_fill_discrete(guide = NULL)+
  geom_label(data = tots2023, aes(x = Type, label = paste("N=", N)), y=5000, inherit.aes = FALSE)+
  theme_bw()

@@

#ANOVA of differences in distance by release group
library(emmeans)
m1 = lm(Distance ~ Type, data = recaps3)
summary(m1)
anova(m1)
emmeans(m1, pairwise ~ Type)
plot(emmeans(m1, pairwise ~ Type), comparisons = T)

#meh

Can cobine Trailer and Large-Scale
Keep carboys seperate
ONly one soft release type

Keep the years togetehr or seperate?

Look at the timing of releases versus number of recaptures. Nov-Dec versus Jan-feb
- Is this all just turbidity? Just at release? or long-term? Pre versus post 'first flush'. We have  a regulatory trigger for when first flush begins. 
- Not all fish are exactly the same age, but they try and realease them all at about the same age, so ones released in November were spawned earlier. 
- Still, check days post hatch

Compare CPUE from EDSM and Salvage

Get data on number released at each event

Soft release in Rio vista in 2022? Check release numbers and timing.

@@

Do we see more recaptures per released fish during different types of releases?

recaps4 = group_by(recaps3, ReleaseEvent, ReleaseDate, Site, Type, Type2, BroodYear) %>%
  summarize(N = n())

releasestat = left_join(release, recaps4) %>%
  filter(Type != "Unknown") %>%
  mutate(BroodYear = as.numeric(str_sub(ReleaseEvent, 3L, end = 6L))) %>%
  left_join(ff) %>%
  mutate(recapsN = case_when(is.na(N) ~0,
                             TRUE ~N),
         RecapRate = recapsN/TotalReleased,
         FFyn = case_when(ReleaseDate > FirstFlush ~ "After First Flush",
                          TRUE ~ "Before First Flush"),
         Type2 = case_when(Type == "Hard (trailer)" ~ "Hard (large scale)",
                           TRUE ~ Type))

totsr = group_by(releasestat, Type2, FFyn) %>%
  summarize(N = n())

ggplot(releasestat, aes(x = Type2, y = RecapRate*100, fill = Type2))+
  geom_boxplot()+
  facet_wrap(~FFyn)+
  ylab("Percentage Recaptured")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust =1, vjust =1),
        legend.position = "none")+
  xlab(NULL)+
  geom_label(data = totsr, aes(x = Type2, label = paste("N=",N)), y = 0, inherit.aes = FALSE)

ggsave("plots/firstflush.tiff", device = "tiff", width =8, height =5)

ggplot(releasestat, aes(x = Type, y = RecapRate*100, color = Type))+
  geom_quasirandom()+
  ylab("Percentage Recaptured")

@@

distances = list(NA)

releasex = filter(release, ReleaseEvent %in% unique(recaps3$ReleaseEvent))
for(i in 1:nrow(releasex)) {
  points = filter(recaps3, ReleaseEvent == releasex$ReleaseEvent[i])
  distances[[i]] = Waterdist(Water_map = spacetools::Delta, Points = points, Latitude_column = `Latitude`,
                    Longitude_column = `Longitude`, PointID_column = FishID)
  names(distances[[i]]) = releasex$ReleaseEvent[i]

}

# RVhdist = Waterdist(Water_map = spacetools::Delta, Points = RVhardt, Latitude_column = `Latitude`,
#                     Longitude_column = `Longitude`, PointID_column = fishID)
# 
# RVhdistx = Waterdist(Water_map = spacetools::Delta, Points = RVhard, Latitude_column = `Latitude`,
#                     Longitude_column = `Longitude`, PointID_column = fishID)
# 
# SCsoft  = Waterdist(Water_map = spacetools::Delta, Points = Dwscsoft, Latitude_column = `Latitude`,
#                        Longitude_column = `Longitude`, PointID_column = fishID)
# 
# SChard = Waterdist(Water_map = spacetools::Delta, Points = Dwschard, Latitude_column = `Latitude`,
#                    Longitude_column = `Longitude`, PointID_column = fishID)

# RVhdist
# RVhdistx
# SCsoft
# SChard

@@

clustest = lapply(distances, function(x){df = data.frame(Mean = mean(x[lower.tri(x)], na.rm =T), SD = sd(x, na.rm =T))} )%>%
  bind_rows() %>%
  mutate(Release = releasex$ReleaseEvent)

clustest
```

@@

alldist = lapply(distances, function(x){
  x[lower.tri(x, diag = T)] = NA
  X = as.data.frame(x) %>%
    mutate(Fish1 = row.names(x)) %>%
    pivot_longer(cols = -Fish1, names_to = "Fish2", values_to = "Distance") %>%
  filter(!is.na(Distance))
  return(X)
})

names(alldist) = releasex$ReleaseEvent

for(i in 1:14) {
  alldist[[i]] = mutate(alldist[[i]], ReleaseEvent = releasex$ReleaseEvent[i])
}

alldist2 = bind_rows(alldist) %>%
  filter(ReleaseEvent != "NA") %>%
  left_join(release)

totsX = group_by(recaps3, ReleaseEvent) %>%
  summarize(N = n())%>%
  filter(ReleaseEvent != "NA")
ggplot(alldist2, aes(x = ReleaseEvent, y = Distance, fill = ReleaseEvent)) + geom_boxplot()+
  ylab("Distance Between Recaptures")+ theme_bw()+ scale_fill_discrete(guide = NULL)+
  theme(axis.text.x = element_text(angle = 45, hjust =1, vjust =1))+
  geom_label(data = totsX, aes(x = ReleaseEvent, y =1, label = paste("N=", N)), fill= "white")

```{r}
alldist2.1 = filter(alldist2, Type != "Unknown") %>%
  mutate(BroodYear = case_when(ReleaseDate < ymd("2023-09-01") ~ 2022,
                               TRUE ~ 2023),
         Type2 = case_when(Type == "Hard (trailer)" ~ "Hard (large scale)",
                           TRUE ~ Type))

ggplot(alldist2.1, aes(x = Type2, y = Distance, fill = Type2)) + geom_boxplot()+
  ylab("Distance Between Recaptures (m)")+
  xlab("Release Type")+
   stat_summary(fun.y=mean, geom="point", shape = 23, fill = "white", size =4) +
  theme_bw() +
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust =1, vjust =1),
        legend.position = "none")

ggsave("plots/DistanceBetweenRecaps.tiff", device = "tiff", width =5, height =4)

ggplot(alldist2.1, aes(x = Type2, y = Distance, fill = Type2)) + geom_boxplot()+
  ylab("Distance Between Recaptures (m)")+
  xlab("Release Type")+
  facet_wrap(~BroodYear)+
   stat_summary(fun.y=mean, geom="point", shape = 23, fill = "white", size =4) +
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust =1, vjust =1),
        legend.position = "none")

ggsave("plots/DistanceBetweenRecaps_byyear.tiff", device = "tiff", width =8, height =5)

@@

The before/after first flush thing was interesting, something with turbidity for the week after the release?

So, first i need to pull turbidity data from that area for the week after each realease.

```{r}
library(cder)
library(zoo)

turbdat = cdec_query("RVB", sensors = 27, start.date = as.Date("2021-01-01"), end.date = today())

turbdat = mutate(turbdat, Month = month(DateTime), Date = date(DateTime), Year = year(DateTime))

turbdat_ave = group_by(turbdat, Date, Month, Year) %>%
  summarize(Turbidity = mean(Value, na.rm =T))

test = rollmean(turbdat_ave$Turbidity, 7, align = "right", na.pad = TRUE)

turbdat_ave$weekturb = test

releasestat = left_join(releasestat, turbdat_ave, by = c("ReleaseDate" = "Date"))

ggplot(filter(releasestat, BroodYear != 2021, Type2 != "NA"), aes(x = weekturb, y = RecapRate )) + geom_point(aes(color = as.factor(BroodYear), shape = Type2), size =3)+ geom_smooth(method = "lm")+ylab("Percentage Recaptured") + 
  xlab("Mean turbidity for 7 days post release (NTU)")+
  theme_bw()+
  scale_color_brewer(palette = "Set2", name = "Brood Year")+
  scale_shape(name = "Release Type")

ggsave("plots/turbidityrecaps.tiff", device = "tiff", width =5, height =4)

## Pretty map of recaputres for presentations

library(tidyverse)
library(lubridate)
library(sf)
library(ggmap)
library(readxl)
library(deltamapr)
library(ggspatial)

smelt = read_excel("Data/smeltcatch_2023.xlsx")

smeltsf = st_as_sf(smelt, coords = c("LongitudeStart", "LatitudeStart"), crs = 4326) %>%
  mutate(Date = str_sub(as.character(SampleDate), 6, 10))

ggplot()+
  geom_sf(data = WW_Delta, fill = "grey90")+
  geom_sf(data = smeltsf, aes(shape = Survey, fill = LifeStage, color = LifeStage), size =5)+
  scale_shape_manual(values = c(23, 24, 25))+
  geom_sf_label(data = smeltsf, aes(label = Date), hjust =0, nudge_x = 0.01)+
  coord_sf(ylim = c(38.0, 38.45), xlim = c(-122.1, -121.55))+
  theme_bw()+
  ylab(NULL)+
  xlab(NULL)+
  annotation_scale()+
  annotation_north_arrow(aes(location = "tl"))

ggsave("Plots/smeltmap2023.tiff", device = "tiff", width =8, height =8)
ggsave("Plots/smeltmap2023.png", device = "png", width =8, height =8)

###########################################################
#map for Katie
smelt2 = read_excel("Data/Running Delta Smelt Catch_2023-09-05.xlsx", sheet = "Delta Smelt Catch Data")

smeltsf = st_as_sf(smelt2, coords = c("LongitudeStart", "LatitudeStart"), crs = 4326) %>%
  mutate(Date = str_sub(as.character(SampleDate), 6, 10)) %>%
  filter(SampleDate > ymd("2023-09-30"))

ggplot()+
  geom_sf(data = WW_Delta, fill = "grey90")+
  geom_sf(data = smeltsf, aes(shape = ReleaseMethod,  fill = ReleaseMethod), size =3)+
  scale_fill_brewer(palette = "Set2", labels = c("Hard (carboy)", "Hard (large scale)", "Hard (trailer)",
                                                  "NA - unmarked fish", "Soft (carboy)"))+
  scale_shape_manual(values = c(21,22,23,24,25), labels = c("Hard (carboy)", "Hard (large scale)", "Hard (trailer)",
                                                  "NA - unmarked fish", "Soft (carboy)"))+
  #geom_sf_label(data = smeltsf, aes(label = Date), hjust =0, nudge_x = 0.01)+
  coord_sf(ylim = c(37.8, 38.35), xlim = c(-122.2, -121.45))+
  theme_bw()+
  ylab(NULL)+
  xlab(NULL)+
  annotation_scale()+
  annotation_north_arrow(aes(location = "tl"))

ggsave("plots/Releasemap.png", device = "png", width =8, height =6)
